Solutions to Integer Programming from Quantum Annealing

### 2020-05-08 paper/main.tex
macbook wants to update... hopefully nothing breaks

\begin{figure*}
	\centering
	\begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.3\textwidth}}
	\includegraphics[width=0.20\textwidth]{./figures/subaru_ds.pdf}
&
	\includegraphics[width=0.20\textwidth]{./figures/subaru_mds4.pdf}
&
	\includegraphics[width=0.20\textwidth]{./figures/subaru_mds2.pdf}\\
	\centering\bf{a} & \centering\bf{b} & \centering\bf{c}
	\end{tabular}
	\caption{Example of different dominating sets for the Pleiades constellation $G(V, E)$. Vertices in the dominating set $D$ are highlighted in blue. {\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 5$. {\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 4$. We note that $D$ is also the maximum independent set of $G$. {\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.}
	\label{fig:dominating_sets}
\end{figure*}

@@

\begin{figure}
	\centering
		\includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
	\caption{
The
	}
	\label{fig:linear}
\end{figure}

We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.

>>>>

\begin{figure*}
	\centering
	\begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.3\textwidth}}
	\includegraphics[width=0.20\textwidth]{./figures/subaru_ds.pdf}
&
	\includegraphics[width=0.20\textwidth]{./figures/subaru_mds4.pdf}
&
	\includegraphics[width=0.20\textwidth]{./figures/subaru_mds2.pdf}\\
	\centering\bf{a} & \centering\bf{b} & \centering\bf{c}
	\end{tabular}
	\caption{Example of different dominating sets for $G(V, E)$. Vertices in the dominating set $D$ are highlighted in blue. {\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 5$. {\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 4$. We note that $D$ is also the maximum independent set of $G$. {\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.}
	\label{fig:dominating_sets}
\end{figure*}

@@

\begin{figure}[b]
	\centering
		\includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
	\label{fig:linear}
\end{figure}

We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}. This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer. Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions. In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
\begin{align}
&1 &&\textrm{if} && n\textrm{ mod }3=0,\nonumber \\
&2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
&\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2.
\end{align}
